### 2017-07-28 README.Rmd
Fix links to vignettes
Note only fixed in Rmd, not compiled

You can read more about visdat in the vignette, ["using visdat""](http://www.njtierney.com/visdat/articles/using_visdat.html).

There are also experimental functions, which include guessing values,  comparing two dataframes, and adding interactivity. These are described in detail in the vignette ["Experimental Features of visdat](http://www.njtierney.com/visdat/articles/experimental_features.html).

>>>>

You can read more about visdat in the vignette, ["using visdat"](http://visdat.njtierney.com/articles/using_visdat.html).

There are also experimental functions, which include guessing values,  comparing two dataframes, and adding interactivity. These are described in detail in the vignette ["Experimental Features of visdat"](http://visdat.njtierney.com/articles/experimental_features.html).
